\documentclass[12pt]{book}
\usepackage[hmargin=0.6in,vmargin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz,lipsum,lmodern}
\usepackage[most]{tcolorbox}

\title{Using fancyhdr for Custom Page Header and Footers in a Two-sided Document}

\usepackage{etoolbox}
\makeatletter
% no new page for \chapter
\patchcmd{\chapter}{\if@openright\cleardoublepage\else\clearpage\fi}{}{}{}
% don't change the pagestyle
\patchcmd{\chapter}{\thispagestyle{plain}}{}{}{%
    % example for a warning, 'Package' in text necessary to make TexStudio show it.
    \GenericWarning{(preamble)\@spaces\@spaces\@spaces\@spaces}{Package preamble Warning: patching \string\chapter\space did not work.}}

% allow floats on top of the page with a new chapter
\patchcmd{\chapter}{\global\@topnum\z@}{}{}{}
% if not commented out, first paragraph will be indented
\patchcmd{\chapter}{\@afterindentfalse}{}{}{}
%\makeatother

\usepackage{titlesec}
\titleformat{\chapter}{\normalfont\bfseries\Large}{\thechapter.\quad}{0pt}{}
\titlespacing{\chapter}{0pt}{-5pt}{4pt}% left space, top space, bottom space



\usepackage{fancyhdr}
% Clear off all default fancyhdr headers and footers
\fancyhf{}
\pagestyle{fancy}

\addtolength{\headheight}{\baselineskip}

\fancyhead[L]{\leftmark}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{#1}}{}}
%\fancyhead[L]{\textbf{\sectiontitle}}
\fancyhead[R]{\sffamily\itshape Lecture Notes on Biophysics}
% Custom text at the left edge of odd pages, and right edge of odd pages.
%\fancyhead[LO,RE]{\sffamily\itshape Fun with fancyhdr}

% Repeat for \fancyfoot if needed, e.g.
% Some decorative symbol at the centre of both odd and even pages
\fancyfoot[L]{\sffamily\itshape Linn Abraham , MGM College of Nursing}
\fancyfoot[C]{\thepage}

\fancyfoot[R]{ June 2020}
% Set this length to 0pt if you don't want any lines!
\renewcommand{\headrulewidth}{2pt}
\pagenumbering{roman}
% Apply the fancy header style


\usepackage{lipsum}
\begin{document}

\title{Heat}
\setcounter{page}{1}
\maketitle
\chapter{Introduction}


\section{Heat}

\subsection*{Nature of Heat}
\begin{enumerate}
    \item Heat is a form of energy.
    \item Heat is energy in transit. 
    \item It is initimately connected with motion. It is the \textbf{total} kinetic energy 
    of the molecules/atoms making up a system. 
    \item Heat always flows from one body to another. The direction is decided by the temperature
    of the two bodies. 
\end{enumerate}
\section{Temperature}
\begin{enumerate}
\item Temperature is a quantitative measure of the heat/thermal energy of a system. 
\item It characterisez the thermal state of a body and determines whether energy will flow 
from or toward it from another body in thermal contact {ref: conduction}.

\end{enumerate}

\subsection{Differences between Heat and Temperature}
 
\section{Effects of Heat on matter}
Expansion and contraction
Phase change
Combustion


\section{Specific heat}

\section{Methods of transfer of heat}
\section{Measurement of Heat and Temperature}
\subsection{Clinical thermometer}
\subsection{Temperature scales}
\section{Relative humidity}
Humidity affects how hot we feel. 
\section{Regulation of body temperature}
Effect of vaporization.
Circulation.

\section{Use of heat for sterilization}
\section{Application in nursing}


\end{document}
